A studyforrest extension, an annotation of spoken language in the German dubbed movie ``Forrest Gump'' and its audio-description

### 2020-05-07 paper/main.tex
Acknowledgment still suitable?

\subsection*{Acknowledgements}
We are grateful to \href{www.florianschurz.de}{Florian Schurz} who initiated doing the annotation of the descriptive nouns, and performed the preliminary annotation of nouns. Christian O. Häusler is also grateful to Valeri Kippes who took care of the author's mental sanity by providing excellent training at his gym in Jülich during the mentally draining period of manual corrections of the annotation.

>>>>

\subsection*{Acknowledgements}
We are grateful to \href{www.florianschurz.de}{Florian Schurz} who initiated doing the annotation of the descriptive nouns\todo{should it still be here? or move in PPA paper?}, and performed the preliminary annotation of nouns. Christian O. Häusler is also grateful to Valeri Kippes who took care of the author's mental sanity by providing excellent training at his gym in Jülich during the mentally draining period of manual corrections of the annotation.
